\documentclass{beamer}

\usetheme{Madrid}

\title{CSE 321 Term Project}
\subtitle{toastune}
\author{Harper Scott}
\institute{University at Buffalo}
\date{Fall 2025}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Introduction}
toastune is...
\begin{itemize}
    \item A real-time system intended to optimize the making of toast.
    \item Portable and intended for use with any toaster on the market.
    \item Responsive, reliable, and easy to setup and use.
\end{itemize}

toastune's goals are to...
\begin{itemize}
    \item Allow the user to consistently toast bread to their desired darkness level.
    \item Be mounted to any toaster in a way that is minimal, versatile, and unobstructive.
    \item Add minimal overhead to the process of toasting a slice of bread.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Features}
Hardware
\begin{itemize}
    \item \textbf{OLED Display:} Shows current toast darkness setting, thermocouple temperature, and idle/run status.
    \item \textbf{Start Button:} Begins the temperature monitoring process.
    \item \textbf{Mode Button:} Changes the toast darkness preference mode.
    \item \textbf{Thermocouple:} Inserted into the toast in order to monitor surface temperature.
    \item \textbf{Servomotor:} Actuates toast cancellation button on toaster when target temperature is attained.
\end{itemize}

Software
\begin{itemize}
    \item Real-time temperature monitoring and servomotor actuation.
    \item State management for the different toast darkness preferences.
    \item Simple, lightweight logic in order to ensure responsiveness and minimize risk of deadline misses.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Challenges}
Hardware Shortcomings
\begin{itemize}
    \item Use of continuous servo limits precision and repeatability.
    \item Display size limits amount of information displayed.
    \item No feasible "universal" servomotor mounting solution could be concieved.
\end{itemize}

Software Limitations
\begin{itemize}
    \item Memory limitations necessitated a shift from a task-based implementation to a simple loop.
    \item The chosen display library only handles text output due to memory constraints.
\end{itemize}

\begin{alertblock}{Warning}
    Currently, toastune carries high risk of electrical shock due to the usage of a bare metal thermocouple.
\end{alertblock}
\end{frame}

\begin{frame}
\frametitle{Roadmap}
Hardware Upgrades
\begin{itemize}
    \item Move from Arduino UNO Rev3 to a more compact board with more memory.
    \item Replace continuous servomotor with a positional servomotor.
    \item Upgrade display for size and potential for different colors.
    \item Use thermocouple that does not present serious electrical risk.
\end{itemize}

Software Changes
\begin{itemize}
    \item Return to a task-based approach to system management.
    \item Implement darkness mode changes when toasting process is ongoing.
    \item Include granular temperature controls.
    \item Add a timer to the display output.
    \item Allow for cancellation of the toast monitoring state.
    \item Improve precision of the servomotor head position.
\end{itemize}
\end{frame}

\end{document}
